### 2022-05-06 paper/ase22/result.tex
result

\jl{The following needs to be in RQ2 result section after simin
  completes RQ2 result section} Table~\ref{table:TestResult} shows
results of evaluation of three \sa models. First column lists
linguistic capability for \sa task, and Columns 2-3 show the number of
seed and expanded test cases respectively. Columns 4-5 show the
failure rate in percentage by running the \sa models on the seed and
expanded test cases respectively. Column 6 shows the number of
expanded test cases failed, but their seed test cases passed. For LC9,
we combine two

From the
table, we can observe that

>>>>

\jl{The following needs to be in RQ2 result section after simin
  completes RQ2 result section} Table~\ref{table:TestResult} shows
results of evaluation of three \sa models. First column lists
linguistic capability for \sa task, and Columns 2-3 show the number of
seed and expanded test cases respectively. Columns 4-5 show the
failure rate in percentage by evaluating the \sa models on the seed
and expanded test cases respectively. Column 6 shows the number of
expanded test cases failed, but their seed test cases passed.  From
the table, we can observe that LC3 has no expanded sentences from its
seeds. It means that the 50 seeds selected in this experiment does not
provide any validated expansions. It is because the randomness of
selection of 50 seeds determines the number of validated
expansions. we expect that more selection of seeds increases the
probability of availability of their expansion. In addition, LC1 and
LC5 obtains 19 and 26 seeds respectively. It represents that \tool
finds and generates their seeds lower than the target number of seeds,
which is 50 in this experiment. In this case, use of larger search
dataset increases the amount of seeds for the \lcs. Finally, we find
that there are number of a number of failed expanded test cases succeeded
before the expansion (pass on seed, but fail on its expanded test
cases). This shows that phase of syntax-based sentence expansion in
\tool captures failure-inducing expansion given a seed. It finally
shows usefulness of \tool since the different test results between seed
and expanded cases provide accurate guidance for debugging model.

### 2022-05-06 paper/ase22/tables/test-results-numbers.tex
result

\DefMacro{test-results-bl-lc7-num-sents}{8528}
\DefMacro{test-results-bl-model0-lc7-num-fail}{43.87}
\DefMacro{test-results-bl-lc3-num-sents}{6786}
\DefMacro{test-results-bl-model0-lc3-num-fail}{11.77}
\DefMacro{test-results-bl-lc4-num-sents}{2496}
\DefMacro{test-results-bl-model0-lc4-num-fail}{97.24}
\DefMacro{test-results-bl-lc6-num-sents}{1000}
\DefMacro{test-results-bl-model0-lc6-num-fail}{86.00}
\DefMacro{test-results-bl-lc5-num-sents}{2124}
\DefMacro{test-results-bl-model0-lc5-num-fail}{88.09}
\DefMacro{test-results-bl-lc2-num-sents}{8000}
\DefMacro{test-results-bl-model0-lc2-num-fail}{21.00}
\DefMacro{test-results-bl-lc0-num-sents}{1716}
\DefMacro{test-results-bl-model0-lc0-num-fail}{77.51}
\DefMacro{test-results-bl-lc1-num-sents}{8658}
\DefMacro{test-results-bl-model0-lc1-num-fail}{0.30}
\DefMacro{test-results-lc9}{Parsing positive and negative sentiment in (question, no) form}
\DefMacro{test-results-bl-lc9-num-sents}{7644}
\DefMacro{test-results-bl-model0-lc9-num-fail}{53.06}
\DefMacro{test-results-bl-lc8-num-sents}{9204}
\DefMacro{test-results-bl-model0-lc8-num-fail}{19.48}
\DefMacro{test-results-bl-model1-lc7-num-fail}{31.57}
\DefMacro{test-results-bl-model1-lc3-num-fail}{3.21}
\DefMacro{test-results-bl-model1-lc4-num-fail}{92.31}
\DefMacro{test-results-bl-model1-lc6-num-fail}{41.60}
\DefMacro{test-results-bl-model1-lc5-num-fail}{20.95}
\DefMacro{test-results-bl-model1-lc2-num-fail}{10.36}
\DefMacro{test-results-bl-model1-lc0-num-fail}{81.06}
\DefMacro{test-results-bl-model1-lc1-num-fail}{1.61}
\DefMacro{test-results-bl-model1-lc9-num-fail}{59.86}
\DefMacro{test-results-bl-model1-lc8-num-fail}{13.71}
\DefMacro{test-results-bl-model2-lc7-num-fail}{41.45}
\DefMacro{test-results-bl-model2-lc3-num-fail}{10.82}
\DefMacro{test-results-bl-model2-lc4-num-fail}{98.16}
\DefMacro{test-results-bl-model2-lc6-num-fail}{86.50}
\DefMacro{test-results-bl-model2-lc5-num-fail}{100.00}
\DefMacro{test-results-bl-model2-lc2-num-fail}{31.65}
\DefMacro{test-results-bl-model2-lc0-num-fail}{96.79}
\DefMacro{test-results-bl-model2-lc1-num-fail}{1.44}
\DefMacro{test-results-bl-model2-lc9-num-fail}{84.25}
\DefMacro{test-results-bl-model2-lc8-num-fail}{16.92}

@@

\DefMacro{test-results-lc9-num-seeds}{100}
\DefMacro{test-results-lc9-num-exps}{2379}
\DefMacro{test-results-model0-lc9-num-seed-fail}{71.00}
\DefMacro{test-results-model0-lc9-num-exp-fail}{72.43}

@@

\DefMacro{test-results-model1-lc9-num-seed-fail}{79.00}
\DefMacro{test-results-model1-lc9-num-exp-fail}{81.84}

@@

\DefMacro{test-results-model2-lc9-num-seed-fail}{93.00}
\DefMacro{test-results-model2-lc9-num-exp-fail}{93.15}
\DefMacro{test-results-model2-lc9-num-pass-to-fail}{12}

>>>>

@@

\DefMacro{test-results-lc10}{Parsing negative sentiment in (question, no) form}
\DefMacro{test-results-lc10-num-seeds}{50}
\DefMacro{test-results-lc10-num-exps}{1161}
\DefMacro{test-results-model0-lc10-num-seed-fail}{100.00}
\DefMacro{test-results-model0-lc10-num-exp-fail}{100.00}
\DefMacro{test-results-model0-lc10-num-pass-to-fail}{0}
\DefMacro{test-results-lc9}{Parsing positive sentiment in (question, no) form}
\DefMacro{test-results-lc9-num-seeds}{50}
\DefMacro{test-results-lc9-num-exps}{1218}
\DefMacro{test-results-model0-lc9-num-seed-fail}{42.00}
\DefMacro{test-results-model0-lc9-num-exp-fail}{46.14}

@@

\DefMacro{test-results-model1-lc10-num-seed-fail}{100.00}
\DefMacro{test-results-model1-lc10-num-exp-fail}{100.00}
\DefMacro{test-results-model1-lc10-num-pass-to-fail}{0}
\DefMacro{test-results-model1-lc9-num-seed-fail}{58.00}
\DefMacro{test-results-model1-lc9-num-exp-fail}{64.53}

@@

\DefMacro{test-results-model2-lc10-num-seed-fail}{94.00}
\DefMacro{test-results-model2-lc10-num-exp-fail}{98.97}
\DefMacro{test-results-model2-lc10-num-pass-to-fail}{4}
\DefMacro{test-results-model2-lc9-num-seed-fail}{92.00}
\DefMacro{test-results-model2-lc9-num-exp-fail}{87.60}
\DefMacro{test-results-model2-lc9-num-pass-to-fail}{8}

### 2022-05-06 paper/ase22/tables/test-results-table.tex
result

\begin{tabular}{p{8.5cm}||cclll}

@@

\multirow{3}{*}{\parbox{8.5cm}{LC1: \UseMacro{test-results-lc0}}}

@@

\multirow{3}{*}{\parbox{8.5cm}{LC2: \UseMacro{test-results-lc1}}}

@@

\multirow{3}{*}{\parbox{8.5cm}{LC3: \UseMacro{test-results-lc2}}}

@@

\multirow{3}{*}{\parbox{8.5cm}{LC4: \UseMacro{test-results-lc3}}}

@@

\multirow{3}{*}{\parbox{8.5cm}{LC5: \UseMacro{test-results-lc4}}}

@@

\multirow{3}{*}{\parbox{8.5cm}{LC6: \UseMacro{test-results-lc5}}}

@@

\multirow{3}{*}{\parbox{8.5cm}{LC7: \UseMacro{test-results-lc6}}}

@@

\multirow{3}{*}{\parbox{8.5cm}{LC8: \UseMacro{test-results-lc7}}}

@@

\multirow{3}{*}{\parbox{8.5cm}{LC9: \UseMacro{test-results-lc8}}}

@@

\multirow{3}{*}{\parbox{8.5cm}{LC10\&11: \UseMacro{test-results-lc9}}}

@@

>>>>

\begin{tabular}{p{8cm}||cclll}

@@

\multirow{3}{*}{\parbox{8cm}{LC1: \UseMacro{test-results-lc0}}}

@@

\multirow{3}{*}{\parbox{8cm}{LC2: \UseMacro{test-results-lc1}}}

@@

\multirow{3}{*}{\parbox{8cm}{LC3: \UseMacro{test-results-lc2}}}

@@

\multirow{3}{*}{\parbox{8cm}{LC4: \UseMacro{test-results-lc3}}}

@@

\multirow{3}{*}{\parbox{8cm}{LC5: \UseMacro{test-results-lc4}}}

@@

\multirow{3}{*}{\parbox{8cm}{LC6: \UseMacro{test-results-lc5}}}

@@

\multirow{3}{*}{\parbox{8cm}{LC7: \UseMacro{test-results-lc6}}}

@@

\multirow{3}{*}{\parbox{8cm}{LC8: \UseMacro{test-results-lc7}}}

@@

\multirow{3}{*}{\parbox{8cm}{LC9: \UseMacro{test-results-lc8}}}

@@

\multirow{3}{*}{\parbox{8cm}{LC10: \UseMacro{test-results-lc9}}}

@@

\multirow{3}{*}{\parbox{8cm}{LC11: \UseMacro{test-results-lc10}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-lc10-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-lc10-num-exps}}
 & BERT$\colon$\UseMacro{test-results-model0-lc10-num-seed-fail}
 & BERT$\colon$\UseMacro{test-results-model0-lc10-num-exp-fail}
 & BERT$\colon$\UseMacro{test-results-model0-lc10-num-pass-to-fail}\\
 & & & RoBERTa$\colon$\UseMacro{test-results-model1-lc10-num-seed-fail}
 & RoBERTa$\colon$\UseMacro{test-results-model1-lc10-num-exp-fail}
 & RoBERTa$\colon$\UseMacro{test-results-model1-lc10-num-pass-to-fail}\\
 & & & dstBERT$\colon$\UseMacro{test-results-model2-lc10-num-seed-fail}
 & dstBERT$\colon$\UseMacro{test-results-model2-lc10-num-exp-fail}
 & dstBERT$\colon$\UseMacro{test-results-model2-lc10-num-pass-to-fail}\\
